Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}

### 2017-02-01 docs/paper/questioning.tex
preprint version

Cross-site scripting
attacks fall into three categories,
{\it non-persistent}
(also known as \emph{reflected}) {\sc xss},
{\it persistent} (also known as \emph{stored}) {\sc xss}
and \textit{Document Object Model} ({\sc dom})
\textit{-based} \textsc{xss}.
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.
{\sc dom}-based {\sc xss} attacks involve
the modification of the {\sc dom} of a webpage.
The {\sc dom} treats an {\sc html} document
as a tree structure where each node is an
object representing a part of the document.
Each object can be accessed and manipulated
programmatically and any visible changes
may then be reflected in the browser.
In a {\sc dom}-based {\sc xss} attack,
the malicious payload
(e.g., hidden in a well-crafted {\sc url}
that is sent to a user via phishing:
\textsc{n-xss} 1.1)
is executed as a result of
the manipulation of the {\sc dom}
environment
(e.g., when another flawed script accesses the
modified {\sc dom} object)
and is not contained in
the {\sc http} response.
That is,
the malicious payload never reaches the server.
Such an attack can be performed
purely client-side across {\sc html} frames.
Hence,
server-side defenses might not be effective
in this case.

@@

    \vspace{-4.8mm}

@@

\vspace{-4mm}

@@

\vspace{-0.3mm}
\section{Recommendations and Lessons Learned}
\label{sec:lessons-learned}
\vspace{-0.3mm}

@@

\vspace{0.5mm}
\noindent\begin{minipage}{0.5\linewidth}
\begin{equation}
\textsc{ppv} = \frac{\textsc{tp}}{\textsc{tp} + \textsc{fp}}
\end{equation}
\end{minipage}
\begin{minipage}{0.5\linewidth}
\begin{equation}
\textsc{npv} = \frac{\textsc{tn}}{\textsc{fn} + \textsc{tn}}
\end{equation}
\end{minipage}\par\vspace{\belowdisplayskip}

\noindent
Equations~\ref{eq:ppv-se-sp} and~\ref{eq:npv-se-sp} use true and false
positives and negatives, like equations~\ref{eq:sensitivity}
and~\ref{eq:specificity}. However, \textsc{tp}, \textsc{tn},
\textsc{fp}, and \textsc{fn} are not qualitatively the same in these two cases:
whereas sensitivity and specificity are measured on a testing
environment, \textsc{ppv} and \textsc{npv} are measured on a real,
production environment. In fact, if \textsc{pr} is the probability of
a particular class of attacks in the real world,
i.e., its prevalence, then we
have~\cite{linn2004}:
\vspace{-1mm}
\begin{equation}
\textsc{ppv} = \frac{\textsc{se}\times \textsc{pr}}{
\textsc{se}\times \textsc{pr} + (1 - \textsc{sp})\times (1 -
\textsc{pr})}
\label{eq:ppv-se-sp}
\end{equation}

\begin{equation}
\textsc{npv} = \frac{\textsc{sp}\times (1 - \textsc{pr})}{
(1 - \textsc{se})\times \textsc{pr} + \textsc{sp}\times (1 -
\textsc{pr})}
\label{eq:npv-se-sp}
\end{equation}
\vspace{-4mm}

@@

\vspace{-0.3mm}
\subsection{Code Availability}
\vspace{-0.7mm}

@@

\vspace{-0.3mm}
\subsection{Performance Overhead,
Deployment and Security Remarks}
\vspace{-0.3mm}

@@

\vspace{-0.3mm}
\section{Conclusion}
\label{sec:conclusion}
\vspace{-0.3mm}

@@

\vspace{-4mm}

\bibliographystyle{IEEEtran}
\bibliography{questioning}
\vspace{-0.5mm}

\section*{Author Biographies}
\vspace{-0.5mm}
\noindent
{\bf Dimitris Mitropoulos} is a Postdoctoral Researcher
in the Computer Science Department
at Columbia University.
He holds a PhD ('14) in Cyber Security from the
Athens University of Economics and Business.
His research interests include application security,
systems security and software engineering.

>>>>

Cross-site scripting
attacks fall into three categories,
{\it non-persistent}
(also known as \emph{reflected}) {\sc xss},
{\it persistent} (also known as \emph{stored}) {\sc xss}
and \textit{Document Object Model} ({\sc dom}) -
\textit{based} \textsc{xss}~\cite{SLMS14}.
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.
{\sc dom}-based {\sc xss} attacks involve
the modification of the {\sc dom} of a webpage.
The {\sc dom} treats an {\sc html} document
as a tree structure where each node is an
object representing a part of the document.
Each object can be accessed and manipulated
programmatically and any visible changes
may then be reflected in the browser.
In a {\sc dom}-based {\sc xss} attack,
the malicious payload
(e.g., hidden in a well-crafted {\sc url}
that is sent to a user via phishing:
\textsc{n-xss} 1.1)
is executed as a result of
the manipulation of the {\sc dom}
environment
(e.g., when another flawed script accesses the
modified {\sc dom} object)
and is not contained in
the {\sc http} response.
That is,
the malicious payload never reaches the server.
Such an attack can be performed
purely client-side across {\sc html} frames.
Hence,
server-side defenses might not be effective
in this case.

@@

    \vspace{-4.6mm}

@@

\vspace{-4.4mm}

@@

\vspace{-0.5mm}
\section{Recommendations and Lessons Learned}
\label{sec:lessons-learned}
\vspace{-0.5mm}

@@

\vspace{0.5mm}
\noindent\begin{minipage}{0.5\linewidth}
\begin{equation}
\textsc{ppv} = \frac{\textsc{tp}}{\textsc{tp} + \textsc{fp}}
\end{equation}
\end{minipage}
\begin{minipage}{0.5\linewidth}
\begin{equation}
\textsc{npv} = \frac{\textsc{tn}}{\textsc{fn} + \textsc{tn}}
\end{equation}
\end{minipage}\par\vspace{\belowdisplayskip}
\vspace{-1.5mm}

\noindent
Equations~\ref{eq:ppv-se-sp} and~\ref{eq:npv-se-sp} use true and false
positives and negatives, like equations~\ref{eq:sensitivity}
and~\ref{eq:specificity}. However, \textsc{tp}, \textsc{tn},
\textsc{fp}, and \textsc{fn} are not qualitatively the same in these two cases:
whereas sensitivity and specificity are measured on a testing
environment, \textsc{ppv} and \textsc{npv} are measured on a real,
production environment. In fact, if \textsc{pr} is the probability of
a particular class of attacks in the real world,
i.e., its prevalence, then we
have~\cite{linn2004}:
\vspace{-1.5mm}
\begin{equation}
\textsc{ppv} = \frac{\textsc{se}\times \textsc{pr}}{
\textsc{se}\times \textsc{pr} + (1 - \textsc{sp})\times (1 -
\textsc{pr})}
\label{eq:ppv-se-sp}
\end{equation}

\begin{equation}
\textsc{npv} = \frac{\textsc{sp}\times (1 - \textsc{pr})}{
(1 - \textsc{se})\times \textsc{pr} + \textsc{sp}\times (1 -
\textsc{pr})}
\label{eq:npv-se-sp}
\end{equation}
\vspace{-4.5mm}

@@

\vspace{-0.6mm}
\subsection{Code Availability}
\vspace{-0.7mm}

@@

\vspace{-0.8mm}
\subsection{Performance Overhead,
Deployment and Security Remarks}
\vspace{-1.3mm}

@@

\vspace{-1mm}
\section{Conclusion}
\label{sec:conclusion}
\vspace{-1mm}

@@

\vspace{-1.5mm}

\section*{Acknowledgements}
\vspace{-1mm}
We would like to thank the anonymous reviewers
for their suggestions and comments.
This work was supported by {\sc nsf} Grant No. {\sc cns}-13-18415.

\vspace{-8mm}

\bibliographystyle{IEEEtran}
\bibliography{questioning}
\vspace{-1.2mm}

\section*{Author Biographies}
\vspace{-1.1mm}
\noindent
{\bf Dimitris Mitropoulos} is a Postdoctoral Researcher
in the Computer Science Department
at Columbia University.
He holds a PhD ('14) in Cyber Security from the
Athens University of Economics and Business.
His research interests include application security,
systems security and software engineering.
